\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr}
\usepackage{enumitem}
\usepackage{booktabs}

\pagestyle{fancy}
\fancyhf{}
\lhead{Team Name: \underline{\hspace{4cm}}}
\rhead{Date: \underline{\hspace{2.5cm}}}
\cfoot{\thepage}

\title{\vspace{-2cm}\textbf{Phase 2: Product Selection \& Survey Design}}
\author{}
\date{}

\begin{document}
\maketitle
\thispagestyle{fancy}

\section*{Part 1: Select Your Client \& Products}
\textbf{Instructions:}
\begin{enumerate}
    \item As a team, choose ONE local business to focus on.
    \item Visit their online menu. Each team member must select a \textbf{different} menu item to analyze.
\end{enumerate}

\begin{center}
\fbox{\begin{minipage}{0.9\textwidth}
\textbf{Team Choice (Circle One):} \quad Golden Monkey \quad | \quad Mandee's Pizza \quad | \quad Yas Chicken
\end{minipage}}
\end{center}

\vspace{0.5cm}

\noindent \textbf{Member Assignments:}
\begin{itemize}[itemsep=10pt]
    \item \textbf{Member 1 Name:} \underline{\hspace{4cm}} \quad \textbf{Item:} \underline{\hspace{5cm}}
    \item \textbf{Member 2 Name:} \underline{\hspace{4cm}} \quad \textbf{Item:} \underline{\hspace{5cm}}
    \item \textbf{Member 3 Name:} \underline{\hspace{4cm}} \quad \textbf{Item:} \underline{\hspace{5cm}}
    \item \textbf{Member 4 Name:} \underline{\hspace{4cm}} \quad \textbf{Item:} \underline{\hspace{5cm}}
    \item \textbf{Member 5 Name:} \underline{\hspace{4cm}} \quad \textbf{Item:} \underline{\hspace{5cm}}
    \item \textbf{Member 6 Name:} \underline{\hspace{4cm}} \quad \textbf{Item:} \underline{\hspace{5cm}}
    \item \textbf{Member 7 Name:} \underline{\hspace{4cm}} \quad \textbf{Item:} \underline{\hspace{5cm}}
\end{itemize}

\section*{Part 2: Design Your Pricing Strategy}
\textbf{Goal:} To find the optimal price, you must test prices \textit{higher} and \textit{lower} than the current menu price.

\begin{enumerate}
    \item \textbf{Current Price:} What does the item cost right now? \$ \underline{\hspace{2cm}}
    \item \textbf{Step Size:} How much will you jump between prices? (e.g., \$0.50 for drinks, \$1.00 for meals) \$ \underline{\hspace{2cm}}
    \item \textbf{Test Prices:} List the 5 prices you will test in your survey.
    \begin{itemize}
        \item Price A (Lowest): \$ \underline{\hspace{2cm}}
        \item Price B: \$ \underline{\hspace{2cm}}
        \item Price C (Current): \$ \underline{\hspace{2cm}}
        \item Price D: \$ \underline{\hspace{2cm}}
        \item Price E (Highest): \$ \underline{\hspace{2cm}}
    \end{itemize}
\end{enumerate}

\section*{Part 3: Survey Construction}
\textbf{Instructions:} You need to ask at least 35 people total (7 people per price point).
Use the script below when asking classmates.

\vspace{0.5cm}

\noindent\textbf{The Script:}
\begin{quote}
\textit{"Hi, my team is analyzing prices for [Business Name]. Would you buy [Item Name] if it cost \$[Price]?"}
\end{quote}

\noindent\textbf{Data Collection Log (Draft):}
\begin{table}[h]
\centering
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Test Price} & \textbf{Tally (Yes)} & \textbf{Tally (No)} & \textbf{Total Yes} \\
\hline
\$ \underline{\hspace{1.5cm}} & & & \\
\hline
\$ \underline{\hspace{1.5cm}} & & & \\
\hline
\$ \underline{\hspace{1.5cm}} & & & \\
\hline
\$ \underline{\hspace{1.5cm}} & & & \\
\hline
\$ \underline{\hspace{1.5cm}} & & & \\
\hline
\end{tabular}
\end{table}

\section*{Part 4: Next Steps (To be completed over the next week)}
\begin{enumerate}
    \item \textbf{Collect Data:} Ask 7 \textit{different} people for each of your 5 price points (35 people total).
    \item \textbf{Record:} Keep a tally of "Yes" answers for each price.
    \item \textbf{Bring Back:} Bring this completed data sheet to class by \underline{\hspace{3cm}}.
\end{enumerate}

\vspace{1cm}
\hrule
\vspace{0.5cm}

\textbf{Teacher Check-In:}
\begin{itemize}
    \item [ ] Client Selected
    \item [ ] Menu Items Assigned
    \item [ ] Pricing Strategy Approved
\end{itemize}

\end{document}
